The non-random assembly of functional motifs in  \nplant-pollinator networks

### 2022-03-29 Manuscript/Main_text/Main_text_Functional_Ecology.Rmd
saving model data to plut it in supplementary mat

To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialization and number of indirect interactions. To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif. Values of the vector $si$, range between 1, complete specialization (1 partner within the motif) and 0 complete generalism (all possible partners within the motif). Then, we calculated the number of indirect interactions for each motif position and trophic guild (i.e., plants or floral visitors) as $z_i-1$ where $z_i$ is the total number of nodes for a trophic guild in a given motif. Because all nodes within a motif are connected, to obtain the total number of indirect interactions for a given position we only have to substract to $z_i$ the motif position of interest that cannot interact indirectly with itself. Finally, we analysed in a single model how specialization and the number of indirect interactions are associated with the observed percentiles for each trophic guild and motif position (see paragraph above). For this, we implemented a GLMM model with the help of the _glmmTMB_ package [@magnusson2017] version _1.0.2.1_ with a Beta distribution because percentiles have exclusively  positive values. The variation at the study system was controlled with the help of the study identifier as a random factor.

>>>>

To understand if the different plant and floral visitor groups are associated with motif positions that represent different network roles, we characterized the roles of each motif positions for plant and floral visitor groups in terms of their specialization and number of indirect interactions. To that end, we calculated the specificity of each motif position following @poisot2015 as $s_i = L - l_i / L - 1$, where $L$ is the total number of groups and $l_i$ the number of interaction partners of the group $i$ in a given motif. Values of the vector $si$, range between 1, complete specialization (1 partner within the motif) and 0 complete generalism (all possible partners within the motif). Then, we calculated the number of indirect interactions for each motif position and trophic guild (i.e., plants or floral visitors) as $z_i-1$ where $z_i$ is the total number of nodes for a trophic guild in a given motif. Because all nodes within a motif are connected, to obtain the total number of indirect interactions for a given position we only have to substract from $z_i$ one unit that corresponds to the position of interest. Finally, we analysed in a single model how specialization and the number of indirect interactions were associated with the observed percentiles for each trophic guild and motif position (see paragraph above). For this, we fitted a LMM model with the help again of the _lmer_ package where we considered specialization and number of indirect interactions as response variables with the interaction by group for the two response variables. This allowed us to explore the individual response for the different plant and floral visitor groups. Further, the variation at the study system was controlled with the help of the study identifier as a random factor.
